---
title: "TO 414 Group Project 2"
author: "Marcus Frankel, Matthew Dugoff, Emily Walker, Nathan Lee, Young-Bin Kim"
date: "12/6/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction of the Problem and Dataset

- The data set in which we are analyzing has 74,111 historic listings on AirBnB. For this project we are focusing solely on the 22,453 LA listings in order to predict the price range within a given city. Variables include both property characteristics like bedrooms and amenities, as well as listing characteristics like average review score and description.
- Business Question: How should LA homeowners set the price of their properties on vacation rental sites?

## Data Cleaning

```{r}
library(class)
library(caret)
library(gmodels)
library(neuralnet)
library(C50)
library(kernlab)
library(lubridate)
library(rpart)
```

```{r, cache=TRUE}
# Import dataset & filter location to LA
airbnb <- read.csv("train.csv")
airbnb <- subset(airbnb, city == "LA")

# Create new columns of amenities
airbnb$amenities_TV <- as.factor(ifelse(grepl("TV", airbnb$amenities) == TRUE, 1, 0))
airbnb$amenities_kitchen <- as.factor(ifelse(grepl("Kitchen", airbnb$amenities) == TRUE, 1, 0))
airbnb$amenities_wifi <- as.factor(ifelse(grepl("Internet", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_pool <- as.factor(ifelse(grepl("Pool", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_AC <- as.factor(ifelse(grepl("Air conditioning", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_gym <- as.factor(ifelse(grepl("Gym", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_heating <- as.factor(ifelse(grepl("Heating", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_hottub <- as.factor(ifelse(grepl("Hot tub", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_lockonbedroomdoor <- as.factor(ifelse(grepl("Lock on bedroom", airbnb$amenities)== TRUE, 1, 0))
airbnb$amenities_parking <- as.factor(ifelse(grepl("Free parking", airbnb$amenities)== TRUE, 1, 0))

# Clean variables
airbnb$host_since <- as.Date(airbnb$host_since)
airbnb$last_review <- as.Date(airbnb$last_review)

airbnb$host_since_month <- as.factor(month(airbnb$host_since))
airbnb$host_since_year <- as.factor(year(airbnb$host_since))
airbnb$last_review_month <- as.factor(month(airbnb$last_review))
airbnb$last_review_year <- as.factor(year(airbnb$last_review))

airbnb$property_type <- as.factor(airbnb$property_type)
airbnb$room_type <- as.factor(airbnb$room_type)
airbnb$bed_type <- as.factor(airbnb$bed_type)
airbnb$cancellation_policy <- as.factor(airbnb$cancellation_policy)
airbnb$cleaning_fee <- as.factor(ifelse(airbnb$cleaning_fee == "True", 1, 0))
airbnb$zipcode <- as.factor(airbnb$zipcode)
airbnb$neighbourhood <- as.factor(airbnb$neighbourhood)

airbnb$host_has_profile_pic <- as.factor(ifelse(airbnb$host_has_profile_pic == "t", 1, 0))
airbnb$host_identity_verified <- as.factor(ifelse(airbnb$host_identity_verified == "t", 1, 0))
airbnb$instant_bookable <- as.factor(ifelse(airbnb$instant_bookable == "t", 1, 0))

airbnb$host_response_rate <- as.numeric(gsub("%", "", as.character(airbnb$host_response_rate)))

airbnb$desc_length <- sapply(strsplit(airbnb$description, " "), length)

# Remove unnecessary variables
airbnb$id <- NULL
airbnb$thumbnail_url <- NULL
airbnb$amenities <- NULL
airbnb$first_review <- NULL
airbnb$latitude <- NULL 
airbnb$longitude <- NULL 
airbnb$name <- NULL
airbnb$city <- NULL
airbnb$description <- NULL
airbnb$host_since <- NULL
airbnb$last_review <- NULL

# Remove NAs
airbnb <- na.omit(airbnb)

# Convert to model matrix
airbnb_mm <- as.data.frame(model.matrix(~.-1, airbnb))

# Normalize
normalize <- function(x) {
  return ((x - min(x)) / (max(x)- min(x)))
}

airbnb_mm[2:560] <- lapply(airbnb_mm[2:560], normalize)

# Remove NaN
airbnb_mm$`property_typeCasa particular` <- NULL
airbnb_mm$property_typeLighthouse <- NULL
airbnb_mm$`property_typeParking Space` <- NULL
airbnb_mm$`property_typeVacation home` <- NULL
airbnb_mm$cancellation_policysuper_strict_30 <- NULL
airbnb_mm$`neighbourhoodAlondra Park` <- NULL
airbnb_mm$neighbourhoodArtesia <- NULL
airbnb_mm$neighbourhoodVernon <- NULL
airbnb_mm$neighbourhoodWilmington <- NULL
airbnb_mm$`neighbourhoodLa Habra` <- NULL
airbnb_mm$zipcode10023 <- NULL
airbnb_mm$zipcode210 <- NULL
airbnb_mm$`zipcode90035-4475` <- NULL
airbnb_mm$zipcode9004 <- NULL
airbnb_mm$zipcode90095 <- NULL
airbnb_mm$`zipcode90403-2638` <- NULL
airbnb_mm$zipcode90631 <- NULL
airbnb_mm$zipcode90701 <- NULL
airbnb_mm$zipcode90840 <- NULL
airbnb_mm$zipcode91308 <- NULL
airbnb_mm$zipcode91740 <- NULL
airbnb_mm$zipcode91786 <- NULL
airbnb_mm$zipcode92614 <- NULL
airbnb_mm$zipcode92880 <- NULL
airbnb_mm$zipcode93105 <- NULL
airbnb_mm$zipcode90630 <- NULL
airbnb_mm$`zipcodeNear 91304` <- NULL

```

## Test and Train Datatsets

```{r}
set.seed(12345)
test_set <- sample(1:nrow(airbnb_mm), 0.7 * nrow(airbnb_mm)) 

airbnb_train <- airbnb_mm[test_set,] 
airbnb_test <- airbnb_mm[-test_set,]

airbnb_train_labels <- airbnb_mm[test_set, "log_price"]
airbnb_test_labels <- airbnb_mm[-test_set, "log_price"]
```

# Analysis

To perform our analysis, we plan to build 5 single level models (linear, KNN, ANN, SVM, and Regression Tree). Next, we will aggregate our predictions from these models to build a combined prediction dataset and use a stacked decision tree model to enhance our findings. 

To gauge our confidence in the models' ability to predict Airbnb listing prices, we will utilize the R-squared and RMSE metrics. A high R-squared value would correlate with a high level of confidence in our model and a low RMSE value highlights low average error across our predictions. 

## Linear Regression

```{r, cache=TRUE}
# First model
airbnb_lm <- lm(log_price ~., data = airbnb_train)

lm_pred <- predict(airbnb_lm, newdata = airbnb_test)

## Result
postResample(lm_pred, airbnb_test$log_price)

# Second model
ctrl <- trainControl(method = "cv", number = 5)

airbnb_lm2 <- train(log_price ~., data = airbnb_train, method = "lm", trControl = ctrl)

lm2_pred <- predict(airbnb_lm2, newdata = airbnb_test)

## Result
postResample(lm2_pred, airbnb_test$log_price)

```

From our linear regression model, we have an R-squared value of 0.7893 and RMSE of 0.3295. 


## KNN

```{r, cache=TRUE}
# Model
knn_train <- airbnb_train[,-match("log_price", names(airbnb_train))]
knn_test <- airbnb_test[,-match("log_price", names(airbnb_test))]

sqrt(nrow(airbnb_train))

knn_pred <- knnregTrain(knn_train, knn_test, airbnb_train_labels, k = 100, use.all = TRUE)

## Result
postResample(knn_pred, airbnb_test$log_price)

```
From our KNN model, we have an R-squared value of 0.5782 and RMSE of 0.5092. 

## ANN

```{r, cache=TRUE}
# First model
names(airbnb_train) <- make.names(names(airbnb_train))
names(airbnb_test) <- make.names(names(airbnb_test))

airbnb_ann <- neuralnet(log_price ~., airbnb_train, stepmax = 1000000, threshold = 0.1, linear.output = TRUE)

ann_results <- compute(airbnb_ann, airbnb_test)
ann_pred <- ann_results$net.result

## Result
postResample(ann_pred, airbnb_test$log_price)
```
From our ANN model, we have an R-squared value of 0.7766 and RMSE of 0.3395. 

## Decision Tree

```{r, cache=TRUE}
# First model
airbnb_dt <- rpart(formula = log_price ~ ., data = airbnb_train, method = "anova")

dt_pred <- predict(airbnb_dt, airbnb_test)

## Result
postResample(dt_pred, airbnb_test$log_price)

# Second model
airbnb_dt2 <- train(log_price ~ ., data = airbnb_train, method = "rpart", trControl = ctrl)

dt2_pred <- predict(airbnb_dt2, airbnb_test)

## Result
postResample(dt2_pred, airbnb_test$log_price)
```

From our regression tree model, we have an R-squared value of 0.5669 and RMSE of 0.4723. 


## SVM 

```{r, cache=TRUE}
# First model
airbnb_svm <- ksvm(log_price ~., data = airbnb_train, kernel = "polydot")

svm_pred <- predict(airbnb_svm, airbnb_test)

## Result
postResample(svm_pred, airbnb_test$log_price)

# Second model
airbnb_svm2 <- ksvm(log_price ~., data = airbnb_train, kernel = "polydot", cross = 5)
svm2_pred <- predict(airbnb_svm2, airbnb_test)

## Result
postResample(svm2_pred, airbnb_test$log_price)
```

From our SVM model using kernel PolyDot, we have an R-squared value of 0.7906 and RMSE of 0.3285579. 

# Stacked Model

## Combined Prediction Table

```{r}
combined_pred <- data.frame(lm2_pred, knn_pred, dt2_pred, ann_pred, svm2_pred, airbnb_test$log_price)
```

## Analysis

```{r, cache=TRUE}
set.seed(12345)
test_set2 <- sample(1:nrow(combined_pred), 0.7 * nrow(combined_pred)) 

airbnb_train2 <- combined_pred[test_set2,] 
airbnb_test2 <- combined_pred[-test_set2,]

# Stacked decision tree model
airbnb_stacked_dt <- rpart(formula = airbnb_test.log_price ~ ., data = airbnb_train2, method = "anova")
airbnb_stacked_dt

stacked_dt_pred <- predict(airbnb_stacked_dt, airbnb_test2)

# Results
postResample(stacked_dt_pred, airbnb_test2$airbnb_test.log_price)


# Trained stacked model
airbnb_stacked_dt2 <- train(airbnb_test.log_price ~ ., data = airbnb_train2, trControl = ctrl, method = "rpart")
stacked_dt_pred2 <- predict(airbnb_stacked_dt2, airbnb_test2)

# Results
postResample(stacked_dt_pred2, airbnb_test2$airbnb_test.log_price)
```



   